Cluster Analysis: Identifying Parkinson's Disease Subtypes

### 2015-06-12 writeup/parkinsons.tex
tablefootnotes in table 3

% CLUSTERS: 2
% ================================
% Root node error: 0.2573624
% Complexity Parameter: 0.01741294
% 10-fold CV error: 0.1241997
% CLUSTERS: 3
% ================================
% Root node error: 0.4571063
% Complexity Parameter: 0.0140056
% 10-fold CV error: 0.1766965
% CLUSTERS: 4
% ================================
% Root node error: 0.5236876
% Complexity Parameter: 0.01222494
% 10-fold CV error: 0.2535211
\begin{table}[ht]
  \centering
  \begin{tabular}{l|l|l|l|l|l}
    K & CP\footnote{Complexity Parameter} & CV Xerror\footnote{10-fold cross
    validation} & Root Feature &
    Root Error & Figure \\
    \hline
    2 & 0.017 & 0.124 & & 0.257 & Figure~\ref{fig:kmeans-dtree-2} \\
    3 & 0.014 & 0.177 & & 0.457 & Figure~\ref{fig:kmeans-dtree-3} \\
    4 & 0.012 & 0.254 & & 0.524 & Figure~\ref{fig:kmeans-dtree-4} \\
  \end{tabular}
  \caption{$k$-kmeans decision trees statistics}
  \label{tab:k-means-dtrees}
\end{table}

>>>>

% CLUSTERS: 2
% ================================
% Root node error: 0.2573624
% Complexity Parameter: 0.01741294
% 10-fold CV error: 0.1241997
% CLUSTERS: 3
% ================================
% Root node error: 0.4571063
% Complexity Parameter: 0.0140056
% 10-fold CV error: 0.1766965
% CLUSTERS: 4
% ================================
% Root node error: 0.5236876
% Complexity Parameter: 0.01222494
% 10-fold CV error: 0.2535211
\begin{table}[ht]
  \centering
  \begin{tabular}{l|l|l|l|l|l}
    K & CP\tablefootnote{Complexity Parameter} & CV Xerror\tablefootnote{10-fold cross
    validation} & Root Feature &
    Root Error & Figure \\
    \hline
    2 & 0.017 & 0.124 & & 0.257 & Figure~\ref{fig:kmeans-dtree-2} \\
    3 & 0.014 & 0.177 & & 0.457 & Figure~\ref{fig:kmeans-dtree-3} \\
    4 & 0.012 & 0.254 & & 0.524 & Figure~\ref{fig:kmeans-dtree-4} \\
  \end{tabular}
  \caption{$k$-kmeans decision trees statistics}
  \label{tab:k-means-dtrees}
\end{table}
